### 2022-03-08 paper/localpsf.tex
paper edits. improved interpolation section a lot

%In Section \ref{sec:intro} we noted that computing $\Aker\left(y,x\right)$ is computationally costly. 
%This section describes how we compute approximate kernel entries
%\begin{equation*}
%\widetilde{\Phi}(y,x) \approx \Phi(y,x)
%\end{equation*}
%for arbitrary pairs of points $(y,x) \in \Omega \times \Omega$. 
Given $(y,x)\in \Omega \times \Omega$, let
\begin{equation}
\label{eq:fxyxp}
f_i := \frac{V(x)}{V(x_i)}\phi_{x_i}\left(y - \mu(x) + \mu(x_i)\right), \qquad i=1,\dots,k,
\end{equation}
%for arbitrary pairs of points $(y,x) \subset \Omega \times \Omega$.
% while Section \ref{sec:approximate_kernel_entries} we showed how we can cheaply evaluate approximate kernel entries at arbitrary pairs of points $(y,x) \in \Omega \times \Omega$.
where $\{x_i\}_{i=1}^k$ are the $k$ nearest sample points to $x$, excluding sample points for which $\phi_{x_i}\left(y - \mu(x) + \mu(x_i)\right)$ is undefined. We approximate $\Phi(y,x)$ by interpolating the (point,value) pairs
\begin{equation}
\left(x_i, f_i\right), \qquad i=1,\dots,k,
\end{equation}
at the point $x$. The idea here is that $\Phi(y,x) = \phi_x(y) \approx \phi_{x_i}\left(y - \mu(x) + \mu(x_i)\right)$ (see Section \ref{eq:local_mean_displacement_invariance}), so we approximate $\Phi(y,x)$ by interpolating the values $\phi_{x_i}\left(y - \mu(x) + \mu(x_i)\right)$. Inclusion of the factor $\frac{V(x)}{V(x_i)}$ in \eqref{eq:fxyxp} is a form of preconditioning that makes this approximation more robust in the case where $V(x)$ varies widely.

To find the $k$ nearest sample points to $x$, we query a precomputed KD-tree \cite{kdtree} of all sample points. The number $k$ is a small user defined parameter; in numerical experiments we use $k=10$. The function $\phi_{x_i}\left(y - \mu(x) + \mu(x_i)\right)$ is defined if and only if $y-\mu(x)+\mu(x_i) \in \Omega$. We check whether $y - \mu(x) + \mu(x_i) \in \Omega$ by querying a precomputed axis aligned bounding box tree (AABB tree) \cite{aabbtree} of the mesh cells used to discretize the problem. 
%Since $\Phi(y,x) \approx f_i$ when $x_i$ is near $x$, we approximate $\Phi(y,x)$ by interpolating the (point,value) pairs
%\begin{equation}
%\left(x_i, f_i\right), \qquad i=1,\dots,k,
%\end{equation}
%at the point $x$. To see that $\Phi(y,x) \approx f_i$, recall from Section \ref{eq:local_mean_displacement_invariance} that $\Phi(y,x) = \phi_x(y) \approx \phi_{x_i}\left(y - \mu(x) + \mu(x_i)\right)$ if $x_i$ is near $x$. Inclusion of the extra factor $\frac{V(x)}{V(x_i)}$ in \eqref{eq:fxyxp} is a form of preconditioning that makes this approximation more robust in the case where $V(x)$ varies widely. 
%Note that we are not in danger of dividing by zero, because our ellipsoid packing procedure from Section \ref{sec:sample_point_selection} excludes $x_i$ from consideration as a sample point if $V(x_i)$ is smaller than a predetermined threshold.
%\subsubsection{Radial basis function interpolation}

@@

We evaluate $f_i$ via the following process. First, we determine whether $y - \mu(x) + \mu(x_i) \in E_{x_i}$ by checking if
\begin{equation}
\label{eq:ellipsoid_check93}
(y - \mu(x_i))^T \Sigma^{-1}(x_i) (y - \mu(x_i))  \le \tau^2.
\end{equation}
If \eqref{eq:ellipsoid_check93} does not hold, then $y - \mu(x) + \mu(x_i)$ is outside the estimated support of $\impulseresponse_{x_i}$, so we set $f_i=0$. If \eqref{eq:ellipsoid_check93} does hold, then we look up the batch index $b$ such that $x_i \in S_b$, and evaluate
\begin{equation}
f_i = V(x)\eta_b\left(y - \mu(x) + \mu(x_i)\right),
\end{equation}
as per \eqref{eq:fxyxp} and \eqref{eq:varphi_eval}.
%Recall from Section \ref{sec:get_impulse_response} that $\eta_b$ is the impulse response batch that we have computed and stored.
%Evaluating $\eta_b\left(y - \mu(x) + \mu(x_i)\right)$ requires care, because

>>>>

%In Section \ref{sec:intro} we noted that computing $\Aker\left(y,x\right)$ is computationally costly. 
%This section describes how we compute approximate kernel entries
%\begin{equation*}
%\widetilde{\Phi}(y,x) \approx \Phi(y,x)
%\end{equation*}
%for arbitrary pairs of points $(y,x) \in \Omega \times \Omega$. 
Given $(y,x)\in \Omega \times \Omega$, let
\begin{equation}
\label{eq:fxyxp}
f_i := \frac{V(x)}{V(x_i)}\phi_{x_i}\left(y - \mu(x) + \mu(x_i)\right), \qquad i=1,\dots,k,
\end{equation}
%for arbitrary pairs of points $(y,x) \subset \Omega \times \Omega$.
% while Section \ref{sec:approximate_kernel_entries} we showed how we can cheaply evaluate approximate kernel entries at arbitrary pairs of points $(y,x) \in \Omega \times \Omega$.
where $\{x_i\}_{i=1}^k$ are the $k$ nearest sample points to $x$, excluding sample points for which $\phi_{x_i}\left(y - \mu(x) + \mu(x_i)\right)$ is undefined. Here $k$ is a small user defined parameter; e.g., $k=10$. We approximate $\Phi(y,x)$ by interpolating the (point,value) pairs
\begin{equation}
\left(x_i, f_i\right), \qquad i=1,\dots,k,
\end{equation}
at the point $x$. The idea is that $\Phi(y,x) = \phi_x(y) \approx \phi_{x_i}\left(y - \mu(x) + \mu(x_i)\right)$ per the discussion in Section \ref{eq:local_mean_displacement_invariance}, so we approximate $\Phi(y,x)$ by interpolating the values $\phi_{x_i}\left(y - \mu(x) + \mu(x_i)\right)$. Inclusion of the factor $\frac{V(x)}{V(x_i)}$ in \eqref{eq:fxyxp} is a form of preconditioning that makes this approximation more robust if $V(x)$ varies widely.

To find the $k$ nearest sample points to $x$, we query a precomputed KD-tree \cite{kdtree} of all sample points. The quantity $\phi_{x_i}\left(y - \mu(x) + \mu(x_i)\right)$ is defined if and only if $y-\mu(x)+\mu(x_i) \in \Omega$. We check whether $y - \mu(x) + \mu(x_i) \in \Omega$ by querying a precomputed axis aligned bounding box tree (AABB tree) \cite{aabbtree} of the mesh cells used to discretize the problem. 
%Since $\Phi(y,x) \approx f_i$ when $x_i$ is near $x$, we approximate $\Phi(y,x)$ by interpolating the (point,value) pairs
%\begin{equation}
%\left(x_i, f_i\right), \qquad i=1,\dots,k,
%\end{equation}
%at the point $x$. To see that $\Phi(y,x) \approx f_i$, recall from Section \ref{eq:local_mean_displacement_invariance} that $\Phi(y,x) = \phi_x(y) \approx \phi_{x_i}\left(y - \mu(x) + \mu(x_i)\right)$ if $x_i$ is near $x$. Inclusion of the extra factor $\frac{V(x)}{V(x_i)}$ in \eqref{eq:fxyxp} is a form of preconditioning that makes this approximation more robust in the case where $V(x)$ varies widely. 
%Note that we are not in danger of dividing by zero, because our ellipsoid packing procedure from Section \ref{sec:sample_point_selection} excludes $x_i$ from consideration as a sample point if $V(x_i)$ is smaller than a predetermined threshold.
%\subsubsection{Radial basis function interpolation}

@@

To evaluate $f_i$, we check whether $y - \mu(x) + \mu(x_i) \in E_{x_i}$ using \eqref{eq:support_ellipsoid}. If $y - \mu(x) + \mu(x_i) \notin E_{x_i}$, then
% by checking if
%\begin{equation}
%\label{eq:ellipsoid_check93}
%(y - \mu(x_i))^T \Sigma^{-1}(x_i) (y - \mu(x_i))  \le \tau^2.
%\end{equation}
%If \eqref{eq:ellipsoid_check93} does not hold, 
then $y - \mu(x) + \mu(x_i)$ is outside the estimated support of $\impulseresponse_{x_i}$, so we set $f_i=0$.
% If \eqref{eq:ellipsoid_check93} does hold, then 
If $y - \mu(x) + \mu(x_i) \in E_{x_i}$, we look up the batch index $b$ such that $x_i \in S_b$, and evaluate
\begin{equation}
f_i = V(x)\eta_b\left(y - \mu(x) + \mu(x_i)\right),
\end{equation}
per \eqref{eq:fxyxp} and \eqref{eq:varphi_eval}.
%Recall from Section \ref{sec:get_impulse_response} that $\eta_b$ is the impulse response batch that we have computed and stored.
%Evaluating $\eta_b\left(y - \mu(x) + \mu(x_i)\right)$ requires care, because
